\documentclass[11pt,]{article}
\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}


  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}




\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center

\renewenvironment{abstract}
 {{%
    \setlength{\leftmargin}{0mm}
    \setlength{\rightmargin}{\leftmargin}%
  }%
  \relax}
 {\endlist}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother




\setcounter{secnumdepth}{0}




\title{Predicting Opinion Change in Deliberative Groups (Natural Language
Processing) \thanks{Code and data available at: github.com/rossdahlke/cs\_230\_project}  }



\author{\Large Ross Dahlke
(\href{mailto:rdahlke@stanford.edu}{\nolinkurl{rdahlke@stanford.edu}})\vspace{0.05in} \newline\normalsize\emph{}  }


\date{}

\usepackage{titlesec}

\titleformat*{\section}{\normalsize\bfseries}
\titleformat*{\subsection}{\normalsize\itshape}
\titleformat*{\subsubsection}{\normalsize\itshape}
\titleformat*{\paragraph}{\normalsize\itshape}
\titleformat*{\subparagraph}{\normalsize\itshape}





\newtheorem{hypothesis}{Hypothesis}
\usepackage{setspace}


% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


% move the hyperref stuff down here, after header-includes, to allow for - \usepackage{hyperref}

\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \PassOptionsToPackage{hyphens}{url}\usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \PassOptionsToPackage{hyphens}{url}\usepackage[draft,unicode=true]{hyperref}
\fi
}

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Ross Dahlke
(\href{mailto:rdahlke@stanford.edu}{\nolinkurl{rdahlke@stanford.edu}}) ()},
             pdfkeywords = {},  
            pdftitle={Predicting Opinion Change in Deliberative Groups (Natural Language
Processing)},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

% Add an option for endnotes. -----


% add tightlist ----------
\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% add some other packages ----------

% \usepackage{multicol}
% This should regulate where figures float
% See: https://tex.stackexchange.com/questions/2275/keeping-tables-figures-close-to-where-they-are-mentioned
\usepackage[section]{placeins}


\begin{document}
	
% \pagenumbering{arabic}% resets `page` counter to 1 
%
% \maketitle

{% \usefont{T1}{pnc}{m}{n}
\setlength{\parindent}{0pt}
\thispagestyle{plain}
{\fontsize{18}{20}\selectfont\raggedright 
\maketitle  % title \par  

}

{
   \vskip 13.5pt\relax \normalsize\fontsize{11}{12} 
\textbf{\authorfont Ross Dahlke
(\href{mailto:rdahlke@stanford.edu}{\nolinkurl{rdahlke@stanford.edu}})} \hskip 15pt \emph{\small }   

}

}






\vskip -8.5pt


 % removetitleabstract

\noindent \singlespacing 

\hypertarget{introduction}{%
\section{1. Introduction}\label{introduction}}

Deliberative Democracy is when a representative sample of people come
together for a short period of time to discuss civic issues. The idea is
that through a deliberative process, where people are access to
objective information and good conditions to discuss, people can come to
conclusions on civic issues that are most representative of what people
actually want {[}cite Fishkin book{]}. In a time where so much
discussion about political and civic issues happens in online
information bubbles, Deliberative Democracy offers a chance for people
to discuss issues on their merit and the freedom to change their
opinions in order to reveal a better representation of public opinion.

Deliberative Democracy Polling is a technique pioneered by Stanford
University Professor Jim Fishkin and the Center for Deliberative
Democracy (CDD). A Deliberative Poll is where individuals are polled on
their opinions before and after a weekend of small-group deliberation.
This method allows researchers to measure the change in people's
opinions as a result of the deliberative sessions.

This project uses the results of surveys and transcripts from the CDD's
Deliberative Polls to predict group opinion change based on the
transcripts from the groups' deliberative sessions. In talking with
members of the CDD, they theorized that computational approaches to
predicting opinion change might be difficult because of the narrow focus
of each of the deliberative sessions. For example, one whole session
might be devoted to discussing water policy. And so, water is the main
topic of discussion the entire time. Folks from the CDD have also
concluded that participants often don't explicitly say that they have
changed their opinion on the topic of the deliberative session, even if
they reveal a change in opinion in the survey. Given this prior
information, I will work on building a model to predict opinion change
in two steps:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  (For this milestone) Experimenting with predicting opinion change
  based on the words and text of the deliberative sessions.
\item
  (For the final submission) Experimenting with predicting opinion
  change by incorporating linguistic features
\end{enumerate}

Based on previous discussions with members of the CDC, I will first try
to find a baseline model based on the text found in the transcripts. For
the final project I will try to incorporate linguistic features into the
models. Incorporating linguistic features will be a key component of
this project because I hypothesize that it is not \emph{what} people
talk about in the deliberative sessions, it is \emph{how} they talk
about the issues that indicates opinion change. For example, how
subjective or objective are the statements people are making in the
deliberative setting, or how are sentences structured in groups that
show opinion change versus don't show opinion change?

\hypertarget{related-work}{%
\section{2. Related work}\label{related-work}}

This project derives its inspiration from two main previous papers:
``Attitude Change on Reddit's Change My View'' (Priniski and Horne 2018)
and ``A Deep-Learning Approach for Identifying Collective Action Events
with Text and Image Data from Social Media'' (Zhang and Pan 2019). The
former paper found that the ``the amount of evidence provided in a
discussion predicts attitude change'' on the Change My View Reddit
forum. The latter paper was able to identify and collective action
events in China based on image and text data and provides inspiration on
using text data to identify collective behavior that has real-world
application and can be a component of future computational social
science research.

\hypertarget{dataset-and-features}{%
\section{3. Dataset and Features}\label{dataset-and-features}}

This project thanks the CDD for sharing their data. For this project, I
have access to surveys and transcripts from three Deliberative Polls,
each consisting of about 14 groups, with each group discussing in two or
three different sessions. The surveys allow me to calculate opinion
change on the issues discussed in each session before and after the
deliberations. I use these pre- and post-surveys (responses on a 1-10
scale) to calculate an average delta in opinion change for each
deliberative group for each topic session which I use as my dependent
variable. The transcripts are broken down by group by session, but they
are not attributed to specific individuals. While the additional
granularity of individually-attributed transcripts would have great and
is something to consider devoting resources to in the future, these
group-level opinion deltas and transcripts provide enough data to
complete the task. In total, there are 101 examples. I break these down
into 71 training examples, 20 validation examples, and 10 test examples.

\hypertarget{methods}{%
\section{4. Methods}\label{methods}}

To capture changes in the differences in the words that disscusants use
through their deliberations, I break each transcript down into 1/10th
chunks. I then calculated the similarity of each 1/10th chunk to each
other by comparing the word embeddings of each chunk {[}spacy{]}. For
example, of a given transcript, there might be a similarity of .9
between the first and second 1/10th chunks and a similarity of .7
between the third and fourth 1/10th chunks. I use these similarities
from each transcript to build two simple OLS models {[}sklearn{]}. The
first baseline model just uses the similarity of the second and tenth
chunks (the first chunk is generally devoted to introductions, welcomes,
etc.) to predict opinion deltas. The second model uses all of the
similarities to try predict opinion deltas. I also train a basic neural
network in Pytorch to try to predict the opinion deltas from all of the
similarities.

In addition to this approach of using word embeddings, I also build a
baseline model using Long short-term memory on the sequences of words in
the transcripts.

\hypertarget{experiments-results-discussion}{%
\section{5. Experiments/ Results/
Discussion}\label{experiments-results-discussion}}

\hypertarget{next-steps}{%
\section{6. Next Steps}\label{next-steps}}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-cmv}{}%
Priniski, John Hunter, and Zach Horne. 2018. ``Attitude Change on
Reddit's Change My View.'' \emph{Conference: Proceedings of the 40th
Annual Meeting of the Cognitiee Science Society, Madison, Wisconsin}.
\url{https://www.researchgate.net/publication/333175400_Attitude_Change_on_Reddit's_Change_My_View}.

\leavevmode\hypertarget{ref-zhang}{}%
Zhang, Han, and Jennifer Pan. 2019. ``CASM: A Deep-Learning Approach for
Identifying Collective Action Events with Text and Image Data from
Social Media.'' \emph{Sociological Methodology} 49 (1): 1--57.





\newpage
\singlespacing 
\end{document}
