---
output:
  pdf_document:
    # citation_package: biblatex
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ../svm-latex-ms.tex
title: "CS 230 Project: Preanalysis"
thanks: "Code and data available at: github.com/rossdahlke/cs_230_project"
author:
- name: Ross Dahlke (rdahlke@stanford.edu)
affiliation: Stanford University
abstract: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
spacing: double
bibliography: ../proposal/bibliography.bib
biblio-style: apsr
---

```{r include = F}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(tidyverse)
```

# The main purpose of this document is to analyze the results of the DPs in order to determine which questions should be used in the analysis.

I will calculate on which issues opinions change the most, or if I can even use an average of all of the questions.

## Ghana

```{r}
ghana_groups <- read_csv("../data/raw/surveys/ghana-mergedataset.csv") %>% 
  select(namerespon, formnumber, groupnumber)

ghana_pre <- read_csv("../data/raw/surveys/ghana-presurvey.csv") %>% 
  mutate_at(vars(starts_with("q")), ~str_replace(., "Extremely important", "10")) %>% 
  mutate_at(vars(starts_with("q")), ~str_replace(., "Exactly in Middle", "5")) %>% 
  mutate_at(vars(starts_with("q")), ~str_replace(., "Extremely Unimportant", "0")) %>% 
  mutate_at(vars(starts_with("q")), ~str_replace(., "99", "5")) %>% 
  mutate_at(vars(starts_with("q")), ~as.numeric(.)) %>% 
  mutate(formnumber = as.character(formnumber)) %>% 
  left_join(ghana_groups %>% select(-namerespon), by = "formnumber")

ghana_post <- read_csv("../data/raw/surveys/ghana-postsurvey.csv") %>% 
  mutate_at(vars(starts_with("q")), ~str_replace(., "Extremely important", "10")) %>% 
  mutate_at(vars(starts_with("q")), ~str_replace(., "Exactly in Middle", "5")) %>% 
  mutate_at(vars(starts_with("q")), ~str_replace(., "Extremely Unimportant", "0")) %>% 
  mutate_at(vars(starts_with("q")), ~str_replace(., "99", "5")) %>% 
  mutate_at(vars(starts_with("q")), ~as.numeric(.)) %>% 
  mutate(formnumber = as.character(formnumber)) %>% 
  left_join(ghana_groups %>% select(-formnumber), by = "namerespon")
```

### Food Safety and Livelihood

The following questions have to do with food safety and livelihood:

  - q3
  - q12
  - q14

```{r}
ghana_pre_summarized <- ghana_pre %>% 
  group_by(groupnumber) %>% 
  summarize(pre_q3 = mean(q3, na.rm = T),
            pre_q12 = mean(q12, na.rm = T),
            pre_q14 = mean(q14, na.rm = T)) %>% 
  mutate(pre_all = (pre_q3 + pre_q12 + pre_q14) / 3)
```

```{r}
ghana_post_summarized <- ghana_post %>% 
  group_by(groupnumber) %>% 
  summarize(post_q3 = mean(q3, na.rm = T),
            post_q12 = mean(q12, na.rm = T),
            post_q14 = mean(q14, na.rm = T)) %>% 
  mutate(post_all = (post_q3 + post_q12 + post_q14) / 3)
```

```{r}
ghana_deltas <- ghana_pre_summarized %>% 
  left_join(ghana_post_summarized) %>% 
  mutate(delta_q3 = post_q3 - pre_q3,
         delta_q12 = post_q12 - pre_q12,
         delta_q14 = post_q14 - pre_q14,
         delta_all = post_all - pre_all) 
```

Looks like the average delta is the same across all, so we can use all the groups.

```{r}
ghana_deltas %>% 
  summarize_at(vars(contains("delta")), ~mean(.)) %>% 
  knitr::kable()
```
```{r}
ghana_deltas %>% 
  select(groupnumber, contains("delta")) %>% 
  pivot_longer(-c(groupnumber)) %>% 
  ggplot(aes(name, value, fill = name)) +
  geom_boxplot() +
  coord_flip() +
  theme_bw() +
  theme(legend.position = "none")
```

## Water policy

The following questions have to do with food safety and livelihood:

  - q5
  - q20
  - q29
  - q33

```{r}
ghana_pre_summarized <- ghana_pre %>% 
  group_by(groupnumber) %>% 
  summarize(pre_q5 = mean(q5, na.rm = T),
            pre_q20 = mean(q20, na.rm = T),
            pre_q29 = mean(q29, na.rm = T),
            pre_q33 = mean(q33, na.rm = T)) %>% 
  mutate(pre_all = (pre_q5 + pre_q20 + pre_q29 + pre_q33) / 4)
```

```{r}
ghana_post_summarized <- ghana_post %>% 
  group_by(groupnumber) %>% 
  summarize(post_q5 = mean(q5, na.rm = T),
            post_q20 = mean(q20, na.rm = T),
            post_q29 = mean(q29, na.rm = T),
            post_q33 = mean(q33, na.rm = T)) %>% 
  mutate(post_all = (post_q5 + post_q20 + post_q29 + post_q33) / 4)
```

```{r}
ghana_deltas <- ghana_pre_summarized %>% 
  left_join(ghana_post_summarized) %>% 
  mutate(delta_q5 = post_q5 - pre_q5,
         delta_q20 = post_q20 - pre_q20,
         delta_q29 = post_q29 - pre_q29,
         delta_q33 = post_q33 - pre_q33,
         delta_all = post_all - pre_all) 
```

The deltas aren't huge here. I'll keep all of the data.

```{r}
ghana_deltas %>% 
  summarize_at(vars(contains("delta")), ~mean(.)) %>% 
  knitr::kable()
```
```{r}
ghana_deltas %>% 
  select(groupnumber, contains("delta")) %>% 
  pivot_longer(-c(groupnumber)) %>% 
  ggplot(aes(name, value, fill = name)) +
  geom_boxplot() +
  coord_flip() +
  theme_bw() +
  theme(legend.position = "none")
```

# Bududa

```{r}
bududa_groups <- foreign::read.dta("../data/raw/surveys/BUD data with group numbers.dta") %>% 
  select(id, groupnumber = GroupNumber)

bududa <- readxl::read_xlsx("../data/raw/surveys/uganda_Deliberative polling_Pre& Post Survey Data.xlsx") %>% 
  janitor::clean_names() %>%
  mutate_at(vars(starts_with("x1")), funs(ifelse(. == 99, 5, .))) 
  

bududa_pre <- bududa %>% 
  filter(str_detect(x000id, "BUD") & x001_poll == 1) %>% 
  left_join(bududa_groups, by = c("x000id" = "id"))

bududa_post <- bududa %>% 
  filter(str_detect(x000id, "BUD") & x001_poll == 2) %>% 
  left_join(bududa_groups, by = c("x000id" = "id"))
```

## Land Management

  - [28] "x114_planttrees_protectriverbeds"        
  - [29] "x115_riverchannels_localgovernment"      
  - [30] "x116_wetlands_dryseason"                 
  - [31] "x117_riceschemes_notinwetlands"          
  - [32] "x118_communities_maintainwaterchannels"  
  - [33] "x119_communities_benefitscropdiversity"  
  - [34] "x120_communities_de_silting"             
  - [35] "x121_government_assistdesilting"         
  - [36] "x122_communities_sanitationdrains"       
  - [37] "x123_government_drillingcleanwater"      
  - [38] "x124_communities_resourcesaccesswater" 

```{r}
bududa_pre_summarized <- bududa_pre %>% 
  group_by(groupnumber) %>% 
  summarize(pre_q114 = mean(x114_planttrees_protectriverbeds, na.rm = T),
            pre_q115 = mean(x115_riverchannels_localgovernment, na.rm = T),
            pre_q116 = mean(x116_wetlands_dryseason, na.rm = T),
            pre_q117 = mean(x117_riceschemes_notinwetlands, na.rm = T),
            pre_q118 = mean(x118_communities_maintainwaterchannels, na.rm = T),
            pre_q119 = mean(x119_communities_benefitscropdiversity, na.rm = T),
            pre_q120 = mean(x120_communities_de_silting, na.rm = T),
            pre_q121 = mean(x121_government_assistdesilting, na.rm = T),
            pre_q122 = mean(x122_communities_sanitationdrains, na.rm = T),
            pre_q123 = mean(x123_government_drillingcleanwater, na.rm = T),
            pre_q124 = mean(x124_communities_resourcesaccesswater, na.rm = T)) %>% 
  mutate(pre_all = (pre_q114 + pre_q115 + pre_q115 + pre_q116 + pre_q117 + pre_q118 + pre_q119 + pre_q120 + pre_q121 + pre_q122 + pre_q123 + pre_q124) / 12)
```

```{r}
bududa_post_summarized <- bududa_post %>% 
  group_by(groupnumber) %>% 
  summarize(post_q114 = mean(x114_planttrees_protectriverbeds, na.rm = T),
            post_q115 = mean(x115_riverchannels_localgovernment, na.rm = T),
            post_q116 = mean(x116_wetlands_dryseason, na.rm = T),
            post_q117 = mean(x117_riceschemes_notinwetlands, na.rm = T),
            post_q118 = mean(x118_communities_maintainwaterchannels, na.rm = T),
            post_q119 = mean(x119_communities_benefitscropdiversity, na.rm = T),
            post_q120 = mean(x120_communities_de_silting, na.rm = T),
            post_q121 = mean(x121_government_assistdesilting, na.rm = T),
            post_q122 = mean(x122_communities_sanitationdrains, na.rm = T),
            post_q123 = mean(x123_government_drillingcleanwater, na.rm = T),
            post_q124 = mean(x124_communities_resourcesaccesswater, na.rm = T)) %>% 
  mutate(post_all = (post_q114 + post_q115 + post_q115 + post_q116 + post_q117 + post_q118 + post_q119 + post_q120 + post_q121 + post_q122 + post_q123 + post_q124) / 12)
```

```{r}
bududa_deltas <- bududa_pre_summarized %>% 
  left_join(bududa_post_summarized) %>% 
  mutate(delta_q114 = post_q114 - pre_q114,
         delta_q115 = post_q115 - pre_q115,
         delta_q116 = post_q116 - pre_q116,
         delta_q117 = post_q117 - pre_q117,
         delta_q118 = post_q118 - pre_q118,
         delta_q119 = post_q119 - pre_q119,
         delta_q120 = post_q120 - pre_q120,
         delta_q121 = post_q121 - pre_q121,
         delta_q122 = post_q122 - pre_q122,
         delta_q123 = post_q123 - pre_q123,
         delta_q124 = post_q124 - pre_q124,
         delta_all = post_all - pre_all) 
```

There's quite a bit of variation across questions. However, it all seems to average out in the "delta_all". So, I'll keep them all for now. 

```{r}
bududa_deltas %>% 
  summarize_at(vars(contains("delta")), ~mean(.)) %>% 
  knitr::kable()
```

```{r}
bududa_deltas %>% 
  select(groupnumber, contains("delta")) %>% 
  pivot_longer(-c(groupnumber)) %>% 
  ggplot(aes(name, value, fill = name)) +
  geom_boxplot() +
  coord_flip() +
  theme_bw() +
  theme(legend.position = "none")
```

## Population pressure

  - [39] "x125_buildroads_accessmarkets"           
  - [40] "x126_government_morebridges"             
  - [41] "x127_government_raisenarrowbridges"      
  - [42] "x128_newbuildings_highfloors"            
  - [43] "x129_communities_ladders"                
  - [44] "x130_government_oneclassschools"         
  - [45] "x131_commties_girlsandboys"              
  - [46] "x132_commties_technicalschools"          
  - [47] "x133_government_enforceminimumageof18"   
  - [48] "x134_resources_planningsizeoffamilies"   
  - [49] "x135_education_familyplanning"           
  - [50] "x136_healthcenter_i_is"                  
  - [51] "x137_moreroads_fewerbridges"             

```{r}
bududa_pre_summarized <- bududa_pre %>% 
  group_by(groupnumber) %>% 
  summarize(pre_q125 = mean(x125_buildroads_accessmarkets, na.rm = T),
            pre_q126 = mean(x126_government_morebridges, na.rm = T),
            pre_q127 = mean(x127_government_raisenarrowbridges, na.rm = T),
            pre_q128 = mean(x128_newbuildings_highfloors, na.rm = T),
            pre_q129 = mean(x129_communities_ladders, na.rm = T),
            pre_q130 = mean(x130_government_oneclassschools, na.rm = T),
            pre_q131 = mean(x131_commties_girlsandboys, na.rm = T),
            pre_q132 = mean(x132_commties_technicalschools, na.rm = T),
            pre_q133 = mean(x133_government_enforceminimumageof18, na.rm = T),
            pre_q134 = mean(x134_resources_planningsizeoffamilies, na.rm = T),
            pre_q135 = mean(x135_education_familyplanning, na.rm = T),
            pre_q136 = mean(x136_healthcenter_i_is, na.rm = T),
            pre_q137 = mean(x137_moreroads_fewerbridges, na.rm = T)) %>% 
  mutate(pre_all = (pre_q125 + pre_q126 + pre_q127 + pre_q128 + pre_q129 + pre_q130 + pre_q131 + pre_q132 + pre_q133 + pre_q134 + pre_q135 + pre_q136 + pre_q137) / 13)
```

```{r}
bududa_post_summarized <- bududa_post %>% 
  group_by(groupnumber) %>% 
  summarize(post_q125 = mean(x125_buildroads_accessmarkets, na.rm = T),
            post_q126 = mean(x126_government_morebridges, na.rm = T),
            post_q127 = mean(x127_government_raisenarrowbridges, na.rm = T),
            post_q128 = mean(x128_newbuildings_highfloors, na.rm = T),
            post_q129 = mean(x129_communities_ladders, na.rm = T),
            post_q130 = mean(x130_government_oneclassschools, na.rm = T),
            post_q131 = mean(x131_commties_girlsandboys, na.rm = T),
            post_q132 = mean(x132_commties_technicalschools, na.rm = T),
            post_q133 = mean(x133_government_enforceminimumageof18, na.rm = T),
            post_q134 = mean(x134_resources_planningsizeoffamilies, na.rm = T),
            post_q135 = mean(x135_education_familyplanning, na.rm = T),
            post_q136 = mean(x136_healthcenter_i_is, na.rm = T),
            post_q137 = mean(x137_moreroads_fewerbridges, na.rm = T)) %>% 
  mutate(post_all = (post_q125 + post_q126 + post_q127 + post_q128 + post_q129 + post_q130 + post_q131 + post_q132 + post_q133 + post_q134 + post_q135 + post_q136 + post_q137) / 13)
```

```{r}
bududa_deltas <- bududa_pre_summarized %>% 
  left_join(bududa_post_summarized) %>% 
  mutate(delta_q125 = post_q125 - pre_q125,
         delta_q126 = post_q126 - pre_q126,
         delta_q127 = post_q127 - pre_q127,
         delta_q128 = post_q128 - pre_q128,
         delta_q129 = post_q129 - pre_q129,
         delta_q130 = post_q130 - pre_q130,
         delta_q131 = post_q131 - pre_q131,
         delta_q132 = post_q132 - pre_q132,
         delta_q133 = post_q133 - pre_q133,
         delta_q134 = post_q134 - pre_q134,
         delta_q135 = post_q135 - pre_q135,
         delta_q136 = post_q136 - pre_q136,
         delta_q137 = post_q137 - pre_q137,
         delta_all = post_all - pre_all) 
```

Again, there's quite a bit of variation. But I'll still keep all of the questions. 

```{r}
bududa_deltas %>% 
  summarize_at(vars(contains("delta")), ~mean(.)) %>% 
  knitr::kable()
```

```{r}
bududa_deltas %>% 
  select(groupnumber, contains("delta")) %>% 
  pivot_longer(-c(groupnumber)) %>% 
  ggplot(aes(name, value, fill = name)) +
  geom_boxplot() +
  coord_flip() +
  theme_bw() +
  theme(legend.position = "none")
```

## Resettlement

  - [15] "x101_rezoning"                           
  - [16] "x102_compesation"                        
  - [17] "x103_resettle_hostfamilies"              
  - [18] "x104_support_hostfamilies"               
  - [19] "x105_strengthen_dm_cs"                          
  - [20] "x106_raisefunds_dm_cs"                   
  - [21] "x107_training_dm_cs"                     
  - [22] "x108_buildperi_urbancenterrs"            
  - [23] "x109_newperi_urbancenters_nearby"  

```{r}
bududa_pre_summarized <- bududa_pre %>% 
  group_by(groupnumber) %>% 
  summarize(pre_q101 = mean(x101_rezoning, na.rm = T),
            pre_q102 = mean(x102_compesation, na.rm = T),
            pre_q103 = mean(x103_resettle_hostfamilies, na.rm = T),
            pre_q104 = mean(x104_support_hostfamilies, na.rm = T),
            pre_q105 = mean(x105_strengthen_dm_cs, na.rm = T),
            pre_q106 = mean(x106_raisefunds_dm_cs, na.rm = T),
            pre_q107 = mean(x107_training_dm_cs, na.rm = T),
            pre_q108 = mean(x108_buildperi_urbancenterrs, na.rm = T),
            pre_q109 = mean(x109_newperi_urbancenters_nearby, na.rm = T)) %>% 
  mutate(pre_all = (pre_q101 + pre_q102 + pre_q103 + pre_q104 + pre_q105+ pre_q106 + pre_q107 + pre_q108 + pre_q109) / 9)
```

```{r}
bududa_post_summarized <- bududa_post %>% 
  group_by(groupnumber) %>% 
  summarize(post_q101 = mean(x101_rezoning, na.rm = T),
            post_q102 = mean(x102_compesation, na.rm = T),
            post_q103 = mean(x103_resettle_hostfamilies, na.rm = T),
            post_q104 = mean(x104_support_hostfamilies, na.rm = T),
            post_q105 = mean(x105_strengthen_dm_cs, na.rm = T),
            post_q106 = mean(x106_raisefunds_dm_cs, na.rm = T),
            post_q107 = mean(x107_training_dm_cs, na.rm = T),
            post_q108 = mean(x108_buildperi_urbancenterrs, na.rm = T),
            post_q109 = mean(x109_newperi_urbancenters_nearby, na.rm = T)) %>% 
  mutate(post_all = (post_q101 + post_q102 + post_q103 + post_q104 + post_q105+ post_q106 + post_q107 + post_q108 + post_q109) / 9)
```

```{r}
bududa_deltas <- bududa_pre_summarized %>% 
  left_join(bududa_post_summarized) %>% 
  mutate(delta_q101 = post_q101 - pre_q101,
         delta_q102 = post_q102 - pre_q102,
         delta_q103 = post_q103 - pre_q103,
         delta_q104 = post_q104 - pre_q104,
         delta_q105 = post_q105 - pre_q105,
         delta_q106 = post_q106 - pre_q106,
         delta_q107 = post_q107 - pre_q107,
         delta_q108 = post_q108 - pre_q108,
         delta_q109 = post_q109 - pre_q109,
         delta_all = post_all - pre_all) 
```

Again, there's quite a bit of variation. But I'll still keep all of the questions. 

```{r}
bududa_deltas %>% 
  summarize_at(vars(contains("delta")), ~mean(.)) %>% 
  knitr::kable()
```

```{r}
bududa_deltas %>% 
  select(groupnumber, contains("delta")) %>% 
  pivot_longer(-c(groupnumber)) %>% 
  ggplot(aes(name, value, fill = name)) +
  geom_boxplot() +
  coord_flip() +
  theme_bw() +
  theme(legend.position = "none")
```

# Butaleja

```{r}
butaleja_groups <- foreign::read.dta("../data/raw/surveys/BUT Data-final.dta") %>% 
  select(id, groupnumber = GroupNumber)

butaleja <- readxl::read_xlsx("../data/raw/surveys/uganda_Deliberative polling_Pre& Post Survey Data.xlsx") %>% 
  janitor::clean_names() %>%
  mutate_at(vars(starts_with("x1")), funs(ifelse(. == 99, 5, .))) 

butaleja_pre <- butaleja %>% 
  filter(str_detect(x000id, "BUT") & x001_poll == 1) %>% 
  left_join(butaleja_groups, by = c("x000id" = "id"))

butaleja_post <- butaleja %>% 
  filter(str_detect(x000id, "BUT") & x001_poll == 2) %>% 
  left_join(butaleja_groups, by = c("x000id" = "id"))
```

## Land Management

  - [28] "x114_planttrees_protectriverbeds"        
  - [29] "x115_riverchannels_localgovernment"      
  - [30] "x116_wetlands_dryseason"                 
  - [31] "x117_riceschemes_notinwetlands"          
  - [32] "x118_communities_maintainwaterchannels"  
  - [33] "x119_communities_benefitscropdiversity"  
  - [34] "x120_communities_de_silting"             
  - [35] "x121_government_assistdesilting"         
  - [36] "x122_communities_sanitationdrains"       
  - [37] "x123_government_drillingcleanwater"      
  - [38] "x124_communities_resourcesaccesswater" 

```{r}
butaleja_pre_summarized <- butaleja_pre %>% 
  group_by(groupnumber) %>% 
  summarize(pre_q114 = mean(x114_planttrees_protectriverbeds, na.rm = T),
            pre_q115 = mean(x115_riverchannels_localgovernment, na.rm = T),
            pre_q116 = mean(x116_wetlands_dryseason, na.rm = T),
            pre_q117 = mean(x117_riceschemes_notinwetlands, na.rm = T),
            pre_q118 = mean(x118_communities_maintainwaterchannels, na.rm = T),
            pre_q119 = mean(x119_communities_benefitscropdiversity, na.rm = T),
            pre_q120 = mean(x120_communities_de_silting, na.rm = T),
            pre_q121 = mean(x121_government_assistdesilting, na.rm = T),
            pre_q122 = mean(x122_communities_sanitationdrains, na.rm = T),
            pre_q123 = mean(x123_government_drillingcleanwater, na.rm = T),
            pre_q124 = mean(x124_communities_resourcesaccesswater, na.rm = T)) %>% 
  mutate(pre_all = (pre_q114 + pre_q115 + pre_q115 + pre_q116 + pre_q117 + pre_q118 + pre_q119 + pre_q120 + pre_q121 + pre_q122 + pre_q123 + pre_q124) / 12)
```

```{r}
butaleja_post_summarized <- butaleja_post %>% 
  group_by(groupnumber) %>% 
  summarize(post_q114 = mean(x114_planttrees_protectriverbeds, na.rm = T),
            post_q115 = mean(x115_riverchannels_localgovernment, na.rm = T),
            post_q116 = mean(x116_wetlands_dryseason, na.rm = T),
            post_q117 = mean(x117_riceschemes_notinwetlands, na.rm = T),
            post_q118 = mean(x118_communities_maintainwaterchannels, na.rm = T),
            post_q119 = mean(x119_communities_benefitscropdiversity, na.rm = T),
            post_q120 = mean(x120_communities_de_silting, na.rm = T),
            post_q121 = mean(x121_government_assistdesilting, na.rm = T),
            post_q122 = mean(x122_communities_sanitationdrains, na.rm = T),
            post_q123 = mean(x123_government_drillingcleanwater, na.rm = T),
            post_q124 = mean(x124_communities_resourcesaccesswater, na.rm = T)) %>% 
  mutate(post_all = (post_q114 + post_q115 + post_q115 + post_q116 + post_q117 + post_q118 + post_q119 + post_q120 + post_q121 + post_q122 + post_q123 + post_q124) / 12)
```

```{r}
butaleja_deltas <- butaleja_pre_summarized %>% 
  left_join(butaleja_post_summarized) %>% 
  mutate(delta_q114 = post_q114 - pre_q114,
         delta_q115 = post_q115 - pre_q115,
         delta_q116 = post_q116 - pre_q116,
         delta_q117 = post_q117 - pre_q117,
         delta_q118 = post_q118 - pre_q118,
         delta_q119 = post_q119 - pre_q119,
         delta_q120 = post_q120 - pre_q120,
         delta_q121 = post_q121 - pre_q121,
         delta_q122 = post_q122 - pre_q122,
         delta_q123 = post_q123 - pre_q123,
         delta_q124 = post_q124 - pre_q124,
         delta_all = post_all - pre_all) 
```

There's quite a bit of variation across questions. However, it all seems to average out in the "delta_all". So, I'll keep them all for now. 

```{r}
butaleja_deltas %>% 
  summarize_at(vars(contains("delta")), ~mean(.)) %>% 
  knitr::kable()
```

```{r}
butaleja_deltas %>% 
  select(groupnumber, contains("delta")) %>% 
  pivot_longer(-c(groupnumber)) %>% 
  ggplot(aes(name, value, fill = name)) +
  geom_boxplot() +
  coord_flip() +
  theme_bw() +
  theme(legend.position = "none")
```


## Population Pressure

  - [39] "x125_buildroads_accessmarkets"           
  - [40] "x126_government_morebridges"             
  - [41] "x127_government_raisenarrowbridges"      
  - [42] "x128_newbuildings_highfloors"            
  - [43] "x129_communities_ladders"                
  - [44] "x130_government_oneclassschools"         
  - [45] "x131_commties_girlsandboys"              
  - [46] "x132_commties_technicalschools"          
  - [47] "x133_government_enforceminimumageof18"   
  - [48] "x134_resources_planningsizeoffamilies"   
  - [49] "x135_education_familyplanning"           
  - [50] "x136_healthcenter_i_is"                  
  - [51] "x137_moreroads_fewerbridges"             

```{r}
butaleja_pre_summarized <- butaleja_pre %>% 
  group_by(groupnumber) %>% 
  summarize(pre_q125 = mean(x125_buildroads_accessmarkets, na.rm = T),
            pre_q126 = mean(x126_government_morebridges, na.rm = T),
            pre_q127 = mean(x127_government_raisenarrowbridges, na.rm = T),
            pre_q128 = mean(x128_newbuildings_highfloors, na.rm = T),
            pre_q129 = mean(x129_communities_ladders, na.rm = T),
            pre_q130 = mean(x130_government_oneclassschools, na.rm = T),
            pre_q131 = mean(x131_commties_girlsandboys, na.rm = T),
            pre_q132 = mean(x132_commties_technicalschools, na.rm = T),
            pre_q133 = mean(x133_government_enforceminimumageof18, na.rm = T),
            pre_q134 = mean(x134_resources_planningsizeoffamilies, na.rm = T),
            pre_q135 = mean(x135_education_familyplanning, na.rm = T),
            pre_q136 = mean(x136_healthcenter_i_is, na.rm = T),
            pre_q137 = mean(x137_moreroads_fewerbridges, na.rm = T)) %>% 
  mutate(pre_all = (pre_q125 + pre_q126 + pre_q127 + pre_q128 + pre_q129 + pre_q130 + pre_q131 + pre_q132 + pre_q133 + pre_q134 + pre_q135 + pre_q136 + pre_q137) / 13)
```

```{r}
butaleja_post_summarized <- butaleja_post %>% 
  group_by(groupnumber) %>% 
  summarize(post_q125 = mean(x125_buildroads_accessmarkets, na.rm = T),
            post_q126 = mean(x126_government_morebridges, na.rm = T),
            post_q127 = mean(x127_government_raisenarrowbridges, na.rm = T),
            post_q128 = mean(x128_newbuildings_highfloors, na.rm = T),
            post_q129 = mean(x129_communities_ladders, na.rm = T),
            post_q130 = mean(x130_government_oneclassschools, na.rm = T),
            post_q131 = mean(x131_commties_girlsandboys, na.rm = T),
            post_q132 = mean(x132_commties_technicalschools, na.rm = T),
            post_q133 = mean(x133_government_enforceminimumageof18, na.rm = T),
            post_q134 = mean(x134_resources_planningsizeoffamilies, na.rm = T),
            post_q135 = mean(x135_education_familyplanning, na.rm = T),
            post_q136 = mean(x136_healthcenter_i_is, na.rm = T),
            post_q137 = mean(x137_moreroads_fewerbridges, na.rm = T)) %>% 
  mutate(post_all = (post_q125 + post_q126 + post_q127 + post_q128 + post_q129 + post_q130 + post_q131 + post_q132 + post_q133 + post_q134 + post_q135 + post_q136 + post_q137) / 13)
```

```{r}
butaleja_deltas <- butaleja_pre_summarized %>% 
  left_join(butaleja_post_summarized) %>% 
  mutate(delta_q125 = post_q125 - pre_q125,
         delta_q126 = post_q126 - pre_q126,
         delta_q127 = post_q127 - pre_q127,
         delta_q128 = post_q128 - pre_q128,
         delta_q129 = post_q129 - pre_q129,
         delta_q130 = post_q130 - pre_q130,
         delta_q131 = post_q131 - pre_q131,
         delta_q132 = post_q132 - pre_q132,
         delta_q133 = post_q133 - pre_q133,
         delta_q134 = post_q134 - pre_q134,
         delta_q135 = post_q135 - pre_q135,
         delta_q136 = post_q136 - pre_q136,
         delta_q137 = post_q137 - pre_q137,
         delta_all = post_all - pre_all) 
```

Again, there's quite a bit of variation. I'm going to remove 137 since it's such an outlier.

```{r}
butaleja_deltas %>% 
  summarize_at(vars(contains("delta")), ~mean(.)) %>% 
  knitr::kable()
```

```{r}
butaleja_deltas %>% 
  select(groupnumber, contains("delta")) %>% 
  pivot_longer(-c(groupnumber)) %>% 
  ggplot(aes(name, value, fill = name)) +
  geom_boxplot() +
  coord_flip() +
  theme_bw() +
  theme(legend.position = "none")
```

## Resettlement

  - [15] "x101_rezoning"                           
  - [16] "x102_compesation"                        
  - [17] "x103_resettle_hostfamilies"              
  - [18] "x104_support_hostfamilies"               
  - [19] "x105_strengthen_dm_cs"                          
  - [20] "x106_raisefunds_dm_cs"                   
  - [21] "x107_training_dm_cs"                     
  - [22] "x108_buildperi_urbancenterrs"            
  - [23] "x109_newperi_urbancenters_nearby"  

```{r}
butaleja_pre_summarized <- butaleja_pre %>% 
  group_by(groupnumber) %>% 
  summarize(pre_q101 = mean(x101_rezoning, na.rm = T),
            pre_q102 = mean(x102_compesation, na.rm = T),
            pre_q103 = mean(x103_resettle_hostfamilies, na.rm = T),
            pre_q104 = mean(x104_support_hostfamilies, na.rm = T),
            pre_q105 = mean(x105_strengthen_dm_cs, na.rm = T),
            pre_q106 = mean(x106_raisefunds_dm_cs, na.rm = T),
            pre_q107 = mean(x107_training_dm_cs, na.rm = T),
            pre_q108 = mean(x108_buildperi_urbancenterrs, na.rm = T),
            pre_q109 = mean(x109_newperi_urbancenters_nearby, na.rm = T)) %>% 
  mutate(pre_all = (pre_q101 + pre_q102 + pre_q103 + pre_q104 + pre_q105+ pre_q106 + pre_q107 + pre_q108 + pre_q109) / 9)
```

```{r}
butaleja_post_summarized <- butaleja_post %>% 
  group_by(groupnumber) %>% 
  summarize(post_q101 = mean(x101_rezoning, na.rm = T),
            post_q102 = mean(x102_compesation, na.rm = T),
            post_q103 = mean(x103_resettle_hostfamilies, na.rm = T),
            post_q104 = mean(x104_support_hostfamilies, na.rm = T),
            post_q105 = mean(x105_strengthen_dm_cs, na.rm = T),
            post_q106 = mean(x106_raisefunds_dm_cs, na.rm = T),
            post_q107 = mean(x107_training_dm_cs, na.rm = T),
            post_q108 = mean(x108_buildperi_urbancenterrs, na.rm = T),
            post_q109 = mean(x109_newperi_urbancenters_nearby, na.rm = T)) %>% 
  mutate(post_all = (post_q101 + post_q102 + post_q103 + post_q104 + post_q105+ post_q106 + post_q107 + post_q108 + post_q109) / 9)
```

```{r}
butaleja_deltas <- butaleja_pre_summarized %>% 
  left_join(butaleja_post_summarized) %>% 
  mutate(delta_q101 = post_q101 - pre_q101,
         delta_q102 = post_q102 - pre_q102,
         delta_q103 = post_q103 - pre_q103,
         delta_q104 = post_q104 - pre_q104,
         delta_q105 = post_q105 - pre_q105,
         delta_q106 = post_q106 - pre_q106,
         delta_q107 = post_q107 - pre_q107,
         delta_q108 = post_q108 - pre_q108,
         delta_q109 = post_q109 - pre_q109,
         delta_all = post_all - pre_all) 
```

Again, there's quite a bit of variation. I _could_ remove 101, but I'll keep it for now.

```{r}
butaleja_deltas %>% 
  summarize_at(vars(contains("delta")), ~mean(.)) %>% 
  knitr::kable()
```

```{r}
butaleja_deltas %>% 
  select(groupnumber, contains("delta")) %>% 
  pivot_longer(-c(groupnumber)) %>% 
  ggplot(aes(name, value, fill = name)) +
  geom_boxplot() +
  coord_flip() +
  theme_bw() +
  theme(legend.position = "none")
```