---
output:
  pdf_document:
    # citation_package: biblatex
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ../svm-latex-ms.tex
title: "CS 230 Project: Preanalysis"
thanks: "Code and data available at: github.com/rossdahlke/cs_230_project"
author:
- name: Ross Dahlke (rdahlke@stanford.edu)
affiliation: Stanford University
abstract: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
spacing: double
bibliography: ../proposal/bibliography.bib
biblio-style: apsr
---

```{r include = F}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(tidyverse)
```

# The main purpose of this document is to analyze the results of the DPs in order to determine which questions should be used in the analysis.

I will calculate on which issues opinions change the most, or if I can even use an average of all of the questions.

## Ghana

```{r}
ghana_groups <- read_csv("../data/raw/surveys/ghana-mergedataset.csv") %>% 
  select(namerespon, formnumber, groupnumber)

ghana_pre <- read_csv("../data/raw/surveys/ghana-presurvey.csv") %>% 
  mutate_at(vars(starts_with("q")), ~str_replace(., "Extremely important", "10")) %>% 
  mutate_at(vars(starts_with("q")), ~str_replace(., "Exactly in Middle", "5")) %>% 
  mutate_at(vars(starts_with("q")), ~str_replace(., "Extremely Unimportant", "0")) %>% 
  mutate_at(vars(starts_with("q")), ~as.numeric(.)) %>% 
  mutate(formnumber = as.character(formnumber)) %>% 
  left_join(ghana_groups %>% select(-namerespon), by = "formnumber")

ghana_post <- read_csv("../data/raw/surveys/ghana-postsurvey.csv") %>% 
  mutate_at(vars(starts_with("q")), ~str_replace(., "Extremely important", "10")) %>% 
  mutate_at(vars(starts_with("q")), ~str_replace(., "Exactly in Middle", "5")) %>% 
  mutate_at(vars(starts_with("q")), ~str_replace(., "Extremely Unimportant", "0")) %>% 
  mutate_at(vars(starts_with("q")), ~as.numeric(.)) %>% 
  mutate(formnumber = as.character(formnumber)) %>% 
  left_join(ghana_groups %>% select(-formnumber), by = "namerespon")
```

### Food Safety and Livelihood

The following questions have to do with food safety and livelihood:

  - q3
  - q12
  - q14

```{r}
ghana_pre_summarized <- ghana_pre %>% 
  group_by(groupnumber) %>% 
  summarize(pre_q3 = mean(q3, na.rm = T),
            pre_q12 = mean(q12, na.rm = T),
            pre_q14 = mean(q14, na.rm = T)) %>% 
  mutate(pre_all = (pre_q3 + pre_q12 + pre_q14) / 3)
```

```{r}
ghana_post_summarized <- ghana_post %>% 
  group_by(groupnumber) %>% 
  summarize(post_q3 = mean(q3, na.rm = T),
            post_q12 = mean(q12, na.rm = T),
            post_q14 = mean(q14, na.rm = T)) %>% 
  mutate(post_all = (post_q3 + post_q12 + post_q14) / 3)
```
```{r}
ghana_deltas <- ghana_pre_summarized %>% 
  left_join(ghana_post_summarized) %>% 
  mutate(delta_q3 = post_q3 - pre_q3,
         delta_q12 = post_q12 - pre_q12,
         delta_q14 = post_q14 - pre_q14,
         delta_all = post_all - pre_all) 
```

Looks like the average delta is the same across all, so we can use all the groups.

```{r}
ghana_deltas %>% 
  summarize_at(vars(contains("delta")), ~mean(.)) %>% 
  knitr::kable()
```


